Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-19 Paper.Rmd
include scatter plot in cause4copula function

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf}
\caption[Testing GOF between noise-copula parameters and estimated population copula parameters with $500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicates good fit between noise and population copulae. \label{fig_Cause4copula_params_GOF_500}}
\end{center}
\end{figure}

* Next, we measured 3 types of correlations (Spearman, Kendall, Pearson) and different types of non-parametric tail-dependence difference (see \nameref{NPA}) for both bivariate noise copula and resultant population copula for $50$ simulations. Then we plotted mean of each measured quantity with standard error against Kendall's Tau of the noise copula family. Fig. \ref{fig_Cause4copula_C_kend} compares the statistics from population copula which was generated by noises drawn from lower tail dependent Clayton copula. It is possible to measure the statistics with variation of Spearman's Rho for any other noise copula family (e.g. see Fig. \ref{SM-fig_Cause4copula_SC_spear}). We also carried out a paired t-test to compute the p-values of each statistic for noise and population data and found that like our first approach (model selection method), here also the nature of tail dependence in noise and populations remained similar but they were not exactly the same except in Pearson correlation coefficient which ensured the Moran effect on the population data caused by environmental noise. (For code see [`Plotter_Cause4copula_stat`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function).

@@

<!--Asymmetric sensitivity and copula structure in populations-->
\textbf{(ii)} On a second note, we intended to see if any specific (lower or upper) tail dependence emerges from a copula of two meta-populations, due to some global environmental factors (like temperature or snowfall) when it is beyond a certain expectation threshold.

@@

We simulated our model (\ref{eq.AS}) for $b=\pm0.1$ , $a=0.2$, $r=0.8$. $10000$ points were generated from each local and global fluctuations to apply on the initial populations and then after simulation we kept only last $1000$ time step of simulated points to plot the population-copula (Fig. \ref{fig_ms_asym_b_0.1}) for a specific functional form of $g$  (For code see [`Simulator_asym_sens`](https://github.com/sghosh89/BIVAN/blob/master/asym_sensitivity.R) function). We also carried out model selection and non-parametric statistical analysis with each copula of Fig. \ref{fig_ms_asym_b_0.1} and summarized our results in Tables \ref{SM-tab_summary_stat_asym_sens} - \ref{SM-tab_stat_npa_asym_4}. Table \ref{SM-tab_summary_stat_asym_sens} represent the model selection results with AIC weights for best fitted copula and normal copula, model averaged lower and upper tail dependence, p-values (both Cramer-von Mises statistic and Kolmogorov-Smirnov statistic) for goodness of fit test. In each case, successful bootstrap was $100\%$. According to our model selection approach, non-normal copulae (with higher AIC weights) were always best-fit with some asymetric tail dependence. Our non-parametric analysis results (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_4}) are consistent with this model selection approach.

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf}
\caption{Effects of asymmetric global noise copula on two habitat patch model (Eq. \ref{eq.AS}) with growth rate $b=\pm0.1$: copula of two populations ($P_{1}, P_{2}$) shaped according to the asymmetry of noise copula\label{fig_ms_asym_b_0.1}}
\end{center}
\end{figure}

@@

This section is attributed to analysis of question \hyperref[Intro]{\textbf{(Q3)}} from \nameref{Intro}. We found that asymmetric tail dependence had **(i)** effects on skewness of spatially averaged time series data. Spatial mean of the time series data extracted that tail dependence from the multivariate data set, if any, and reflected in the averaged skewness. Because of overall distinct tail dependence of the multivariate copula structure, the skewness of the spatially-averaged time-series data, changed significantly from the individual skewness of time-series data. To test null hypothesis $H_{0}$ which presumed that multivariate copula actually came from normal copula structure, we generated $10000$ number of surrogate normal copula from a given multivariate copula keeping the marginal distribution and the correlation (spearman or kendall) same. Then we calculated the skewness of spatially averaged surrogate time series data, as we did with the actual multivariate data set (For code see [skewness_multivar_dataset.R](https://github.com/sghosh89/BIVAN/blob/master/skewness_multivar_dataset.R)). We made a histogram of surragate skewness and found if actual skewness were within $95\%$ confidence interval or not. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence (and henceforth significantly different skewness than Normal copula).

We also showed **(ii)** asymmetric copula structure affected slope of spatial Taylor's Law differently than as expected from symmetric Normal copula (For details see Appendix \ref{SM-Consequence_TL_simulation}). For example, our model simulation showed lower tail dependent Clayton copula had much higher slope (spatial-Taylor's law) than symmetric Normal copula, which in turn had higher slope than upper tail dependent Survival Clayton family (Fig. \ref{SM-fig_spTL}(I)). Finally, we studied **(iii)** the effects of environmental noise, having a non-Normal copula, on extinction risk (calculated after 25 years) with two metapopulation model, namely, Lewton-Cohen model and Ricker model (For details see Appendix \ref{SM-Consequence_ext_risk}). We considered patches were arranged in a linear chain fashion and the population may disperse to its nearerst two neighbors (local dispersion) or to any patches (global dispersion). For both model with both dispersion, increasing number of habitat patches and increasing carrying capacity, separately, had decreased extinction risk of the populations which was expected (Fig. \ref{SM-fig_risk_numlocs_effect_local_disp} - Fig. \ref{SM-fig_risk_K_effect}). For Lewton-Cohen model, we found greater extinction risk if populations were affected by left tail dependence environmental noise copula than right tail dependent one. For Ricker model, we got the similar observation for smaller values of $r$, the intrinsic growth rate, but for higher values of $r$, there was a turn-over in extinction risks, and right tail dependent noise copula caused population go extinct faster.

@@

we used our four multivariate datasets : aphid-count data, aphid-firstflight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. Figure \ref{fig_skewness_spearman} represents the results for each dataset with Spearman correlation preserving surrogates. We tested null hypothesis $(H_{0})$ which presumed that multivariate copula actually came from normal copula structure with no tail dependence and thus should have the same skewness as of normal copula. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence (and henceforth significantly different skewness than Normal copula).

Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by red dot) was much lower than expected if the aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the non-parametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was much higher than expected if the aphid first flight data came from a normal copula. As $p$ value (the fraction of surrogate-skewness which were greater than the averaged skewness of the given data - red dot in Figure \ref{fig_skewness_spearman} B) was less than $0.05$, we reject $H_{0}$ in support of upper tail dependence, which was also confirmed by model selection and non-parametric results(see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on non-parametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was lower than expected if the data came from a normal copula (Figure \ref{fig_skewness_spearman} D). As $p<0.05$, we rejected $H_{0}$ and that result too was consistent with the non-parametric analysis and model selection results which also favored lower tail dependence (see last column of Table \ref{tab_multivar_summary}).

We carried out the same analysis with aphid abundance and aphid firstflight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal.

We found the same result when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}).

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf}
\caption{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_500}}
\end{center}
\end{figure}

* Next, we measured 3 types of correlations (Spearman, Kendall, Pearson) and different types of non-parametric tail-dependence difference (see \nameref{NPA}) for both bivariate noise copula and resultant population copula (following model \ref{eq.AR1}) for $50$ simulations. Then we plotted mean of each measured quantity with standard error against Kendall's Tau of the noise copula family. Fig. \ref{fig_Cause4copula_C_kend} compares the statistics from population copula and the copula made of noises drawn from lower tail dependent Clayton family. It is possible to measure the statistics with variation of Spearman's Rho for any other noise copula family (e.g. see Fig. \ref{SM-fig_Cause4copula_SC_spear}). We also carried out a paired t-test to compute the p-values of each statistic for noise and population data and found that like our first approach (model selection method), here also the nature of tail dependence in noise and populations remained similar but they were not exactly the same except in Pearson correlation coefficient which ensured the Moran effect on the population data caused by environmental noise. (For code see [`Plotter_Cause4copula_stat`](https://github.com/sghosh89/BIVAN/blob/master/Cause4copula.R) function).

@@

<!--Asymmetric sensitivity and copula structure in populations-->
\textbf{(ii)} On a second note, we intended to see if any specific (lower or upper) tail dependence emerges from a copula of two meta-populations, due to some global environmental factors (like temperature or snowfall) when it is beyond a certain expectation threshold behaves differently.

@@

We simulated our model (\ref{eq.AS}) for $b=0.1$ , $a=0.2$, $r=0.8$. $10000$ points were generated from each local and global fluctuations to apply on the initial populations and then after simulation we kept only last $1000$ time step of simulated points to plot the population-copula (Fig. \ref{fig_ms_asym_b_0.1}) for a specific functional form of $g$  (For code see [`Simulator_asym_sens`](https://github.com/sghosh89/BIVAN/blob/master/asym_sensitivity.R) function). When asymmetric global noise
had only non-positive contributions at two habitat patches ($g_{1}$ in the first panel of Fig. \ref{fig_ms_asym_b_0.1}), lower tail dependence appeared in the global noise copula and so thus in affected population copula (last subplot in the first panel of Fig. \ref{fig_ms_asym_b_0.1}). Similarly, when global noises having only non-negative contributions at two habitat patches ($g_{2}$ in the second panel of Fig. \ref{fig_ms_asym_b_0.1}), upper tail dependence appeared in the global noise copula and so thus in the outcome population copula (last subplot in the second panel of Fig. \ref{fig_ms_asym_b_0.1}). We also carried out model selection and non-parametric statistical analysis with each copula of Fig. \ref{fig_ms_asym_b_0.1} and summarized our results in Tables \ref{SM-tab_summary_stat_asym_sens} - \ref{SM-tab_stat_npa_asym_2}. According to our model selection approach (Table \ref{SM-tab_summary_stat_asym_sens}), non-normal copulae (with higher AIC weights) were always best-fit with similar asymetric tail dependence which gave the support of our hypothesis of the effect of asymmetric global noise copula on populations. Our non-parametric analysis results (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_2}) were consistent with the model selection approach.

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.1_r_0.8_asym_sens.pdf}
\caption{Effects of asymmetric global noise copula on two habitat patch model (Eq. \ref{eq.AS}) with growth rate $b=0.1$: copula of two populations ($P_{1}, P_{2}$) shaped according to the asymmetry of noise copula\label{fig_ms_asym_b_0.1}}
\end{center}
\end{figure}

@@

This section is attributed to analysis of question \hyperref[Intro]{\textbf{(Q3)}} from \nameref{Intro}. We found that asymmetric tail dependence had **(i)** effects on skewness of spatially averaged time series data. Because of overall distinct tail dependence of the multivariate copula structure, the skewness of the spatially-averaged time-series data, changed significantly from the individual skewness of time-series data. To test null hypothesis $H_{0}$ which presumed that multivariate copula actually came from normal copula structure, we generated $10000$ number of surrogate normal copula from a given multivariate copula keeping the marginal distribution and the correlation (spearman or kendall) same. Then we calculated the skewness of spatially averaged surrogate time series data, as we did with the actual multivariate data set (For code see [skewness_multivar_dataset.R](https://github.com/sghosh89/BIVAN/blob/master/skewness_multivar_dataset.R)). We made a histogram of surragate skewness and found if actual skewness were within $95\%$ confidence interval or not. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence (and henceforth significantly different skewness than Normal copula).

We also showed **(ii)** asymmetric copula structure affected slope of spatial Taylor's Law differently than as expected from symmetric Normal copula (For details see Appendix \ref{SM-Consequence_TL_simulation}). For example, our model simulation showed lower tail dependent Clayton copula had much higher slope (spatial-Taylor's law) than symmetric Normal copula, which in turn had higher slope than upper tail dependent Survival Clayton family (Fig. \ref{SM-fig_spTL}(I)).

In the following section we will show application of these ideas with real datasets.
<!-- Extinction risk results are not shown currently, it is introduced as a future idea in Discussion-----------
Finally, we studied **(iii)** the effects of environmental noise, having a non-Normal copula, on extinction risk (calculated after 25 years) with two metapopulation model, namely, Lewton-Cohen model and Ricker model (For details see Appendix \ref{SM-Consequence_ext_risk}). We considered patches were arranged in a linear chain fashion and the population may disperse to its nearerst two neighbors (local dispersion) or to any patches (global dispersion). For both model with both dispersion, increasing number of habitat patches and increasing carrying capacity, separately, had decreased extinction risk of the populations which was expected (Fig. \ref{SM-fig_risk_numlocs_effect_local_disp} - Fig. \ref{SM-fig_risk_K_effect}). For Lewton-Cohen model, we found greater extinction risk if populations were affected by left tail dependence environmental noise copula than right tail dependent one. For Ricker model, we got the similar observation for smaller values of $r$, the intrinsic growth rate, but for higher values of $r$, there was a turn-over in extinction risks, and right tail dependent noise copula caused population go extinct faster. -->

@@

We used our four multivariate datasets : aphid-count data, aphid-firstflight data, plankton data and methane-flux data, to compute skewness of spatially averaged data. We tested null hypothesis $(H_{0})$ which presumed that multivariate copula actually came from normal copula structure with no tail dependence and thus should have the same skewness as of normal copula. If $p$-value is less than $0.05$, then we reject the null hypothesis in support of significant tail dependence (and henceforth significantly different skewness than Normal copula). We carried out the same analysis with aphid abundance and aphid firstflight date data for all 20 aphid species and plankton abundance data for all 22 plankton species. In each study, we got $>5\%$ positive results which gave us confidence in validating significantly different skewness for asymmetric copula than Normal. We found the same result when we repeated our simulation with Kendall correlation preserving surrogates (see Fig. \ref{SM-fig_skewness_kendall}). For example, Figure \ref{fig_skewness_spearman} represents the results for each dataset with Spearman correlation preserving surrogates. Figure \ref{fig_skewness_spearman}(A) showed that averaged skewness (indicated by red dot) was much lower than expected if the aphid count data came from a normal copula. In that example, $p$ value was denoted by the fraction of surrogate-skewness which were lower than the averaged skewness of the given data. As $p<0.05$, we rejected $H_{0}$ in support of significantly stronger lower tail dependence which was also consistent with the non-parametric analysis and model fitting results (see first column of Table \ref{tab_multivar_summary}). On the other hand, Figure \ref{fig_skewness_spearman}(B) demonstrated that averaged skewness was much higher than expected if the aphid first flight data came from a normal copula. As $p$ value (the fraction of surrogate-skewness which were greater than the averaged skewness of the given data - red dot in Figure \ref{fig_skewness_spearman} B) was less than $0.05$, we reject $H_{0}$ in support of upper tail dependence, which was also confirmed by model selection and non-parametric results(see second column of Table \ref{tab_multivar_summary}). Figure \ref{fig_skewness_spearman}(C) showed that averaged skewness was lower than expected if the plankton data came from a normal copula. Our previous results on non-parametric analysis and model fitting also supported lower tail dependence (see third column of Table \ref{tab_multivar_summary}). But, as $p>0.05$, we could not reject $H_{0}$ in that case. Finally, for methane-flux data, the averaged skewness was lower than expected if the data came from a normal copula (Figure \ref{fig_skewness_spearman} D). As $p<0.05$, we rejected $H_{0}$ and that result too was consistent with the non-parametric analysis and model selection results which also favored lower tail dependence (see last column of Table \ref{tab_multivar_summary}).

### 2018-10-19 SupportingInformation.Rmd
include scatter plot in cause4copula function

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Testing GOF between noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicates good fit between noise and population copulae. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}

@@

<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/asym_sens_results/a_0.2_b_0.9_r_0.8_asym_sens.pdf}
\caption[asym sensitivity results : copula plot]{asym sensitivity results : copula plot \label{fig_ms_asym_b_0.9}}
\end{center}
\end{figure}-->

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[,c(1:4)]
rownames(summary_stat)<-c("bestcop.AICw","N.AICw","relLTdep.AICw","relUTdep.AICw","p.CvM","p.KS","BS.success.percent")
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asymmetric sensitivity : \\textbf{bestcop.AICw} and \\textbf{N.AICw} represent the AIC-weightage for best fit copula and Normal copula, \\textbf{relLTdep.AICw} and \\textbf{relLTdep.AICw} represent relative lower tail and upper tail dependence based on AIC-weightage respectively, \\textbf{p.CvM} and \\textbf{p.KS} are the p-values coming from goodness of fit test (Cramer-von Mises and Kolmogorov-Smirnov statistics based), \\textbf{BS.success.percent} percentage of successful bootstraps in goodness of fit test. Each column summarizes those statistics for each copula plotted in Fig. \\ref{MT-fig_ms_asym_b_0.1}.\\label{tab_summary_stat_asym_sens}")
```

@@

\newpage
```{r tab_stat_npa_asym_1,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[1]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[1]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_1}"))
```

@@

```{r tab_stat_npa_asym_3,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[3]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[3]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_3}"))
```

```{r tab_stat_npa_asym_4,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[4]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[4]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_4}"))
```

<!--
```{r tab_stat_npa_asym_5,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[5]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[5]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_5}"))
```

```{r tab_stat_npa_asym_6,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[6]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[6]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_6}"))
```

```{r tab_stat_npa_asym_7,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[7]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[7]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_7}"))
```

```{r tab_stat_npa_asym_8,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[8]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[8]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_8}"))
```
-->
<!--
# Cause of non-Normal copula structure : Asymmetric sensitivity and copula structure in populations \label{Cause_asym_sens}
-->

<!--results='hide'-->
```{r skewness_aphidcount_allsp_plot, echo=F, results="hide", warning=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

@@

<!--
## Extinction risk
        ----moved to Paper.Rmd----
-->

@@

![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with local dispersion (see Eq. \ref{eq.extrisk_model}); numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp}](./Results/ext_risk_local_disp.pdf){ width=40%, height=40% }

@@

![Extinction risk as calculated after 25 years on Ricker model (r=0.25, numsims=10000) decreases as carrying capacity $K$ increases for both local and global dispersion (see Eq. \ref{eq.extrisk_model}).\label{fig_risk_K_effect}](./Results/ext_risk_K_effect.pdf){ width=40%, height=40% }

@@

@@

In order to study the effects of non-Normal copula structure on extinction risk for metapopulations with different dispersal rules, we examined the following generalized multiple patch model where local population dynamics at each patch were governed by the Lewton-Cohen model ($r=0$) or Ricker model ($r \neq 0$) as the case may be;
<!--did I write correct spelling for lewton model?-->

@@

With increasing number of patches from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Fig. \ref{fig_risk_numlocs_effect_local_disp} - Fig. \ref{fig_risk_numlocs_effect_global_disp}] for both model.

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}

@@

```{r tab_summary_stat_asym_sens,echo=F,results="markup"}
summary_stat<-summary_stat[,c(1:2)]
rownames(summary_stat)<-c("bestfit.copula.AICw","Normal.copula.AICw","LT.model.avg","UT.model.avg","p.CvM","p.KS","BS.success.percent")
knitr::kable(summary_stat, booktabs = T, 
             format = "pandoc",
             digits=3,
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption="summary of model selection results for asymmetric sensitivity : \\textbf{bestfit.copula.AICw} and \\textbf{Normal.copula.AICw} represent the AIC-weightage for best fit copula and Normal copula, \\textbf{LT.model.avg} and \\textbf{UT.model.avg} represent AIC-weight based model averaged lower and upper tail dependence respectively, \\textbf{p.CvM} and \\textbf{p.KS} are the p-values coming from goodness of fit test (Cramer-von Mises and Kolmogorov-Smirnov statistics based), \\textbf{BS.success.percent} percentage of successful bootstraps in goodness of fit test. Each column summarizes those statistics for each copula plotted in Fig. \\ref{MT-fig_ms_asym_b_0.1}.\\label{tab_summary_stat_asym_sens}")
```

@@

```{r tab_stat_npa_asym_1,echo=F,results="markup"}
temp<-make_table_stat_fn(data=tab_asym[[1]])
knitr::kable(temp, booktabs = T, 
             format = "pandoc",
      #caption.short = "Results for tests of whether asymmetry of tail dependence was significant compared to a normal-copula null hypothesis.",
      caption =paste(cnm[1]," : A table entry $<N$(or $>N$) indicates the value of the given statistic on the data was less (or more) than its value on $N$ of the surrogates, so entries of the form $<X$ (or $>X$) for $X$ equal to $975$ or above indicate that upper-tail (or lower-tail) dependence was significantly stronger than lower-tail dependence.\\label{tab_stat_npa_asym_1}"))
```

@@

<!--
# Cause of non-Normal copula structure : Asymmetric sensitivity and copula structure in populations \label{Cause_asym_sens}
-->

```{r skewness_aphidcount_allsp_plot, echo=F, results="hide", warning=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("skewness_multivar_dataset.R"),mtime("ncsurrog.R"),mtime("SkewnessAnd3CentMom.R"))}

@@

@@

<!-- Extinction risk results are not shown currently, it is introduced as a future idea in Discussion-->
<!--
![Effect of non-Normal environmental noise copula on extinction risk after 25 years (Lewton-Cohen model : $r=0$, Ricker model : $r\neq0$) with local dispersion (see Eq. \ref{eq.extrisk_model}); numlocs=5, numsteps=25, numsims=10000\label{fig_risk_local_disp}](./Results/ext_risk_local_disp.pdf){ width=40%, height=40% }

@@

![Extinction risk as calculated after 25 years on Ricker model (r=0.25, numsims=10000) decreases as carrying capacity $K$ increases for both local and global dispersion (see Eq. \ref{eq.extrisk_model}).\label{fig_risk_K_effect}](./Results/ext_risk_K_effect.pdf){ width=40%, height=40% }
-->

@@

<!-- Extinction risk results are not shown currently, it is introduced as a future idea in Discussion------

@@

In order to study the effects of non-Normal copula structure on extinction risk for metapopulations with different dispersal rules, we examined the following generalized multiple patch model where local population dynamics at each patch were governed by the Lewton-Cohen model ($r=0$) or Ricker model ($r \neq 0$) as the case may be;

@@

With increasing number of patches from $5$ to $25$, extinction risk decreased [for a fixed $d$] ; [see Fig. \ref{fig_risk_numlocs_effect_local_disp} - Fig. \ref{fig_risk_numlocs_effect_global_disp}] for both model. -->
